---
title: "Getting Data Project"
author: "DataTrail Team"
output: html_notebook
---

# Getting Data Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?>

## Set up

We are going to use this R package (we'll talk more about package in a later chapter).

```{r}
library(readr)
library(magrittr)
library(googlesheets4)
library(dplyr)
library(ggplot2)
```

## Set up directories

Here we are going to make a data directory if it doesn't already exist.

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```

## Getting the data

Here we are reading in a Google spreadsheet with information about leanpub books and their prices. We will read this data in using the googlesheets4 R package.

Assign the URL of your leanpub googlesheet the name `link` and make sure to put quotes around it. Copy and paste it from GoogleSheets exactly.

```{r, solution = TRUE}
# Paste your URL to your googlesheet below! Make sure to put quotes around it
### Your code here
```

We'll read in the data using the code below. You will need to follow the prompt to authorize the data to be read in using your Google login credentials.

```{r}
if (interactive()) {
  ## Get data from your Google sheet
  leanpub_df <-  read_sheet(link, col_types = "c")
} else { 
  # Or if we already have the sheet but no access to credentials let's read it in from here
  if (file.exists(file.path("data", "leanpub_data.csv"))) {
    leanpub_df <- readr::read_csv(file.path("data", "leanpub_data.csv"))
  }
}
```

So we have a snapshot of what this data look like at the time that we ran this analysis (and for easier sharing purposes), let's use the `readr::write_csv()` function to write this to a file.

Save this file to the `data` directory that we created. And name the file `leanpub_data.csv`. If you don't remember how to use the `readr::write_csv()` function, recall you can look it up using `?readr::write_csv`.

```{r, solution = TRUE}
### Your code here
```

## Explore the data

Use some of the functions you learned to investigate your `leanpub_df`. How many dimensions is it? 

```{r, solution = TRUE}
### Your code here
```

What kind of class object is it?

```{r, solution = TRUE}
### Your code here
```

## Cleaning the data

For the upcoming code, we will need to make sure that we have columns named *exactly* `title`, `readers`, `suggested` and `minimum`.

```{r}
# If all four of our required columns are found, then this will print out TRUE
all(c('title', 'readers', 'suggested', 'minimum') %in% colnames(leanpub_df))
```

If the above prints out false, you may want to return to your Googlesheets, rename the columns accordingly and start from the top of this notebook again.

This code will clean your data for you.

```{r}
leanpub_df <- leanpub_df %>%
  mutate_at(dplyr::vars(readers, suggested, minimum),
                         as.numeric)
```

Now that the data are being treated as numeric values properly, we can obtain some summary statistics for your `leanpub_df` dataset. Use a function we have discussed to do this.

```{r, solution = TRUE}
### Your code here
```

## Plotting the data

To investigate our question, we will want to investigate any potential relationship between the number of readers for a book and the suggested price. We will plot these data in the form of a scatterplot. In upcoming chapters we will go into more detail about how to make plots yourself.  

```{r}
ggplot(leanpub_df, aes(readers, suggested)) +
  geom_point(color = "blue") +
  theme_minimal()
```

## Get the stats

Is there a relationship between `readers` and `suggested` price? We can also use a correlation to ask this question.

```{r}
cor.test(leanpub_df$readers, leanpub_df$suggested)
```
If the p value reported is very very small, then there might be a relationship. But also it is likely you'll need to collect more data to get a more confident conclusion using this test.

### Conclusion

Write up your thoughts about this data science project here and answer the following questions:

- What did we find out about our questions?
- How did we explore our questions?
- What did our explorations show us?
- What follow up data science questions arise for you regarding this candy dataset now that we've explored it some?

## Print out session info

Session info is a good thing to print out at the end of your notebooks so that you (and other folks) referencing your notebooks know what software versions and libraries you used to run the notebook.

```{r}
sessionInfo()
```
