---
title: "Stats Project"
author: "DataTrail Team"
output: html_notebook
---

# Stats Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?> 

## Set up 

Let's load these packages for use. 

```{r}
## you can add more, or change...these are suggestions
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(corrplot)
library(knitr)
```

## Set up directories

Here we are going to make a data directory if it doesn't already exist. 

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
if (!dir.exists("plots")) {
  dir.create("plots")
}
```


## Get the data 

In a previous project in `03_Cleaning_Data`, we cleaned a dataset about countries and saved this to an RDS file. 
Read in this file from its location in the `03_Cleaning_Data` folder. **Hint** you will need to use a `..` to backout of this current folder and reference the parent folder of `05_Get_Stats`. 

```{r}

```

Use functions we have discussed previously to see remind yourself of what vairables are ih `countries_df`. 

```{r}

```

### Cleaning the datasets 

We're going to select down to columns we are interested in.  Note that we are also shortening some of the names of these variables so that they fit into graphs more easily. 

```{r}
countries_df <- countries_df %>% 
  select(country, 
         pop = population_in_thousands_2017, 
         pop_density = population_density_per_km2_2017, 
         sex_ratio = sex_ratio_m_per_100_f_2017, 
         gdp = gdp_per_capita_current_us, 
         labour_force_participation_female_male_pop_percent, 
         urban_perc = urban_population_percent_of_total_population, 
         growth_rate = population_growth_rate_average_annual_percent, 
         fertility = fertility_rate_total_live_births_per_woman, 
         life_exp_female = life_expectancy_at_birth_females, 
         life_exp_male =life_expectancy_at_birth_males, 
         infant_mortality = infant_mortality_rate_per_1000_live_births, 
         seats_held_women = seats_held_by_women_in_national_parliaments_percent, 
         pop_using_improved_drinking_water_urban_rural_percent)
```


There are some variables here that need to be split up into two columns much like we did before in `03_Cleaning_the_Data`. 

Repeat the steps we used in that project for the following columns: 

`labour_force_participation_female_male_pop_percent`
`pop_using_improved_drinking_water_urban_rural_percent`     

```{r}

```

Now all of the data in our set, except for `country`, should be numeric, but it isn't necessarily. Use `mutate_at` but exclude `country` and try to use as.numeric on all the other variables. **Hint** you will need an argument that specifies `vars(-country)` to exclude the `country` column. 

```{r}

```

Save this version of your data to an RDS file in this project. 

```{r}

```

## Plot the data 

Let's explore what kinds of distributions these variables have?

Use ggplot2::geom_density() to do this for at least 5 variables of your choice in `countries_df`. 

### Density plot 1 

```{r}

```

### Density plot 2 

```{r}

```

### Density plot 3

```{r}

```

### Density plot 4

```{r}

```

### Density plot 5

```{r}

```

## Run stats  

For this project, we are going to run some exploratory stats. 
 
Use the `cor()` function to create a correlation matrix of all the numeric variables in `countries_df`. You still need to use the argument `use = "complete.obs"`. You will also need to exclude the `country` column from this analysis since it is not numeric.  

Call this correlation matrix `cor_matrix`. 

```{r}

```

Make a table out of this correlation matrix using the `kable()` function. 

```{r}

```

Use the corrplot::corrplot() function to make a correlation matrix from these data. 

```{r}
plot <- corrplot(cor_matrix, type = "upper", order = "hclust", 
                 tl.col = "black")
```

What do you think about the interaction and groupings of these variables? Is there anything surprising? 

Save your plot using the following code. Replace `FILEPATH TO WHERE IT SHOULD BE SAVED` with a file path that will save the plot to our `plots` folder with an appropriate file name. 


```{r}
png(`FILEPATH TO WHERE IT SHOULD BE SAVED`) 
plot
dev.off()
```

### Further exploration 

Based on the plot above, do some statistics and a plot to further explore the relationship of two of the variables in `countries_df`. 

```{r}
# Make a plot of your choice here 
```

```{r}
# Run a statistical test of your choice here
```

### Conclusion 

Write up your thoughts about this data science project here and answer the following questions: 

- What have you learned about the relationship of the two variables you chose? 
- Was anything surprising or confusing? 
- What alternative hypothetical explanations are there for the observed relationships you are seeing? (Remember about third variable problem means you can't say things are causal by correlations) 
- In a hypothetical future study, what questions would you want to explore and what kind of data would you want to use to do this exploration? 

## Print out session info

Session info is a good thing to print out at the end of your notebooks so that you (and other folks) referencing your notebooks know what software versions and libraries you used to run the notebook.

```{r}
sessionInfo()
```
