---
title: "Cleaning Data Project"
author: "DataTrail Team"
output: html_notebook
---

# Cleaning Data Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?> 

## Set up 

Let's load these packages for use. 

```{r}
## you can add more, or change...these are suggestions
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

## Set up directories

Here we are going to make a data directory if it doesn't already exist. 

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```


## Get the data 

In a previous project in `03_Cleaning_Data`, we cleaned a dataset about countries and saved this to an RDS file. 
Read in this file from its location in the `03_Cleaning_Data` folder. **Hint** you will need to use a `..` to backout of this current folder and reference the parent folder of `05_Get_Stats`. 

```{r}
# Read in the dataset for un_df
countries_df <- read_rds(file.path("..", "03_Cleaning_Data", "data", "countries_df.rds"))
```

Use functions we have discussed previously to see remind yourself of what vairables are ih `countries_df`. 

```{r}
colnames(countries_df)
```

### Cleaning the datasets 

```{r}


```

## Plot the data! 


```{r}

  cor(countries_df %>% select(is.numeric), na.rm = TRUE)
  
```


### Conclusion 

Write up your thoughts about this data science project here and answer the following questions: 

- What did we find out about our questions? 
- How did we explore our questions? 
- What did our explorations show us? 
- What follow up data science questions arise for you regarding this candy dataset now that we've explored it some? 

## Print out session info

Session info is a good thing to print out at the end of your notebooks so that you (and other folks) referencing your notebooks know what software versions and libraries you used to run the notebook.

```{r}
sessionInfo()
```
