---
title: "Data Visualization Project"
author: "Data Treal Team"
output: html_document
---

# Data Visualization Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?> 

## Set up 

Let's load these packages for use. Add or subtract from this list as you see fit.

```{r setup, include=FALSE}
## load packages
library(janitor)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(readr)
```


## Set up directories

Here we are going to make a data directory if it doesn't already exist. 

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```

## Get the data 

The data we'll be using for this part of the project are about Airbnbs and can be downloaded from here: https://www.kaggle.com/datasets/arianazmoudeh/airbnbopendata

First, we'll read the data in from our `data/raw` directory. Use the `read_csv` function to do this. Call this new data frame `airbnb_df`. 

```{r}
airbnb_df <- readr::read_csv(file.path("data", "raw", "Airbnb_Open_Data.csv"))
```

Use this chunk to do some exploring of this dataset to get an idea of what kind of information is here. 

```{r}
colnames(airbnb_df)
dim(airbnb_df)
```

### Clean the data 

Use the `janitor::clean_names` function to clean up some of these column names 

```{r}
airbnb_df <- janitor::clean_names(airbnb_df) 
```

### Fix `neighbourhood_group` variable

Take a look at the `neighbourhood_group` variable. Try to summarize how many different neighborhood groups there are. 

```{r}
summary(airbnb_df$neighbourhood_group)
```

You will find that this variable is a character, so we will need to coerce it to a factor to get meaningful information about the groups here.

```{r}
summary(as.factor(airbnb_df$neighbourhood_group))
```

You'll notice there's some typos here `brookln` and `manhatan`. Fix these typos in this dataset by whatever method you find most intuitive. After you have fixed the typos, make sure that you coerce `neighbourhood_group` as a factor. 

```{r}
airbnb_df <- airbnb_df %>% 
  mutate(neighbourhood_group = case_when(
    neighbourhood_group == "brookln" ~ "Brooklyn",
    neighbourhood_group == "manhatan" ~ "Manhattan",
    TRUE ~ neighbourhood_group), 
    neighbourhood_group = as.factor(neighbourhood_group)
    ) 
```

Re-run `summary()` on the `neighbourhood_group` to see if your code successfully fixed these misspellings. 

```{r}
summary(airbnb_df$neighbourhood_group) 
```
### Fix numeric data

The `service_fee` and `price` columns are really numeric data but are being treated as characters because there are `$` and `,` included. 

We'll need to get rid of these. **Hint** use this kind of code: 
`stringr::str_remove(service_fee, "\\$|,")` within a mutate to get rid of the dollar signs. After you get rid of the dollar signs from both `service_fee` and `price`, coerce both of these variables to be numeric. 

```{r}
airbnb_df <- airbnb_df %>% 
  mutate(service_fee = stringr::str_remove(service_fee, "\\$|,"), 
         price = stringr::str_remove(price, "\\$|,"), 
         service_fee = as.numeric(service_fee), 
         price = as.numeric(price))
```

Use summary to see if `price` and `service_fee` are now appropriately numeric data. 

```{r}
summary(airbnb_df$price)
```

```{r}
summary(airbnb_df$service_fee)
```

## Plot the data

Let's make a series of plots that explore how the price of an airbnb may be related to the other variables in this set. 

To refresh your memory, a basic ggplot code looks like this
```
DATA_FRAME %>% 
  ggplot(aes(VARIABLE, VARIABLE, color = OPTIONAL_VARIABLE)) + 
  geom_PLOT_TYPE()
```

We recommend keeping the ggplot2 cheatsheet handy while you are going through this project: 
https://www.rstudio.com/resources/cheatsheets/

### Scatter plot 

Now make a scatter plot that explores if `price` is related to one of the other numeric variables in the dataset. 

```{r}
airbnb_df %>% 
  ggplot(aes(price, reviews_per_month, color = neighbourhood_group)) + 
  geom_point() + 
  theme_bw()
```

### Violin plot 

Make a violin plot for the price distribution of different neighborhood groups. 

```{r}
airbnb_df %>% 
  ggplot(aes(price, neighbourhood_group, fill = neighbourhood_group)) + 
  geom_violin() + 
  theme_bw()
```

### Barplot 

Now make a plot that explores if there's a particular `room_type` that has a higher price than others. You may choose to summarize the `price` by the `room_type`.   

```{r}
airbnb_df %>% 
  group_by(room_type) %>% 
  summarize(avg_price = mean(price, na.rm = TRUE)) %>% 
  ggplot(aes(room_type, avg_price, fill = room_type)) + 
  geom_bar(stat = "identity") + 
  theme_minimal()
```

### Your choice plot! 

Make one more plot that is completely your choice about what variables you'd like to see the relationships of. 

See http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html for inspiration and ideas 

```{r}
airbnb_df %>% 
  ggplot(aes(price)) + 
  geom_density() + 
  theme_minimal() + 
  facet_wrap(~neighbourhood_group)
```

### Conclusion 

Write up your thoughts about this data science project here and answer the following questions: 

- What did we find out about our questions? 
- How did we explore our questions? 
- What did our explorations show us? 
- What follow up data science questions arise for you regarding this candy dataset now that we've explored it some? 

## Print out session info

Session info is a good thing to print out at the end of your notebooks so that you (and other folks) referencing your notebooks know what software versions and libraries you used to run the notebook.

```{r}
sessionInfo()
```
