---
title: "Data Visualization Project"
author: "Data Treal Team"
output: html_document
---

# Data Visualization Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?> 

## Set up 

Let's load these packages for use. Add or subtract from this list as you see fit. 

```{r setup, include=FALSE}
## load packages
library(janitor)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(readr)
```


## Set up directories

Here we are going to make a data directory if it doesn't already exist. 

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```

## Get the data 

The data we'll be using for this part of the project were downloaded from [kaggle](https://www.kaggle.com/aaronschlegel/seattle-pet-licenses/data), and include information about "pet licenses issued by the Seattle Animal Shelter between 2005 and early 2017." 

First, we'll read the data in from our `data/raw_data` directory. Use the read_csv function to do this. Call this new data frame `pet_df`. 

### Airbnb 

Using these data: 
You can get the airbnb dataset here: https://www.kaggle.com/datasets/arianazmoudeh/airbnbopendata

```{r}
airbnb_df <- readr::read_csv(file.path("data", "Airbnb_Open_Data.csv"))
if (!"janitor" %in% installed.packages()){
  install.packages("janitor")
}
airbnb_df <- janitor::clean_names(airbnb_df) %>% 
  # some cleaning
  dplyr::mutate(service_fee = as.numeric(gsub("\\$", "", service_fee)), 
                price = as.numeric(gsub("\\$", "", price)), 
                neighbourhood_group = case_when(
                  neighbourhood_group == "brookln" ~ "Brooklyn",
                  neighbourhood_group == "manhatan" ~ "Manhattan",
                  TRUE ~ neighbourhood_group)
                ) %>% 
  # Remove rows that don't have a price listed
  dplyr::filter(!is.na(price))
```

```{r}
summary(airbnb_df$price)
```

```{r}
airbnb_df %>% 
  ggplot(aes(price, color = neighbourhood_group)) + 
  geom_density() + 
  theme_minimal()
```

```{r}
# Make a plot with airbnb_df
airbnb_df %>% 
  ggplot(aes(neighbourhood_group, price)) + 
  geom_violin()
```

```{r}
airbnb_df %>% 
  ggplot(aes(price, number_of_reviews)) + 
  geom_point() + 
  theme_minimal()
```


```{r}
airbnb_df %>% 
  dplyr::mutate(review_rate_number = as.factor(review_rate_number)) %>%
  ggplot(aes(review_rate_number, price, color = neighbourhood_group)) + 
  geom_violin() + 
  theme_minimal()
```

## Session Info 

```{r}
sessionInfo()
```
