---
title: "Data Visualization Project"
author: "Data Treal Team"
output: html_document
---

# Data Visualization Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?> 

## Set up 

Let's load these packages for use. Add or subtract from this list as you see fit. 

```{r setup, include=FALSE}
## load packages
library(janitor)
library(ggplot2)
library(dplyr)
library(lubridate)
library(zoo)
library(forcats)
library(ggthemes)
library(readr)
```


## Set up directories

Here we are going to make a data directory if it doesn't already exist. 

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```

## Get the data 

The data we'll be using for this part of the project were downloaded from [kaggle](https://www.kaggle.com/aaronschlegel/seattle-pet-licenses/data), and include information about "pet licenses issued by the Seattle Animal Shelter between 2005 and early 2017." 

First, we'll read the data in from our `data/raw_data` directory. Use the read_csv function to do this. Call this new data frame `pet_df`. 

```{r pet-data, warning=FALSE} 
pet_df <- read_csv(file.path("data", "raw", "seattle_pet_licenses.csv"))
```
## Explore the Data

Use functions we have discussed in this course to explore your new data frame, `pet_df`. 

```{r } 
summary(pet_df)
```
## Reformat the Data 





## Visualize the Data

Create a barplot from these data that will illustrate the most common pet names. 

```{r pet-barchart, warning=FALSE} 
ggplot(pet_df, aes(animal_s_name)) +
  geom_bar()
```

```{r pet-cat-table, warning=FALSE} 
## Table: Most frequent Cat Name 
pets %>% 
  filter(species=="SPECIES", animal_s_name != "") %>%
  group_by(VARIABLE) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>%
  top_n(n = 10) %>%
  knitr::kable(., caption = "Top 10 Cat Names in Seattle")
```

```{r pet-dog-table, warning=FALSE} 
## Table: Most frequent Dog Name
## ADD CODE!
```

```{r pet-linechart, warning=FALSE} 
## add date and ym columns
pets$date <- lubridate::ymd_hms(pets$license_issue_date)
pets$ym <- as.yearmon(pets$date, "%y%m")

## how the number of licenses recorded has changed over time
pets %>%
  ## group by yearmonth (`ym`)
  function_name(VARIABLE) %>% 
  ## count number within each group
  function_name(n=n()) %>%
  ggplot(., aes(VARIABLE, n)) + 
  ## geom name for line chart
  geom_GEOM() +
  scale_x_yearmon() + 
  xlab("") + 
  ylab("Number of licenses")
```

```{r pet-plot, warning=FALSE} 
### Explore the data -- create your own plot!

```

# Part 2: Explanatory Data Analysis

The data used in this part of the project were dowloaded from [FiveThirtyEight](https://data.fivethirtyeight.com/) - `steak-survey`.  They were originally used in the article: [How Americans Like Their Steak](https://fivethirtyeight.com/features/how-americans-like-their-steak/). The goal of this part of the project will be to recreate the data visualization used in this article.

## The Data

```{r meat-data, warning=FALSE} 
## read in the data
steak <- read.csv("data/raw_data/steak-risk-survey.csv", stringsAsFactors = FALSE) %>%
  ## remove first row which just includes the word "Response" in each column
  slice(2:n())
```

## Explore the Data

```{r meat-explore, warning=FALSE} 
## Include code here to explore the data 
## and answer the questions in the exercise
```

## Wrangle the Data

```{r meat-wrangle, warning=FALSE} 
## wrangle the steak data set
pref <- steak %>% 
  mutate(steak_pref = factor(How.do.you.like.your.steak.prepared.,
                             levels = c("Well",
                                        "Medium Well",
                                        "Medium",
                                        "Medium rare",
                                        "Rare"))) %>% 
  filter(steak_pref != "") %>% 
  group_by(steak_pref) %>% 
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))
```

## Visualize the Data

```{r meat-visualize, warning=FALSE}
## generate the plot 
p <- ggplot(pref) +
  ## specify you want to generate a bar chart
  function_name(aes(x = steak_pref, y = prop, fill = steak_pref),
                stat = 'identity', 
                width = 0.7) + 
  ## this adds text labels (you don't have to change anything here)
  geom_text(aes(label = paste0(as.integer(prop*100),"%"),
                x = steak_pref,
                y = prop), 
            stat= "identity", 
            hjust = -0.2, 
            size = 5,
            color = "grey40") +
  ## flip coordinates to make horizontal box plot
  function_name() +
  ## change the colors of the bars
  function_name(values = c("#370B01", 
                           "#70402C",
                           "#955732", 
                           "#B36153",
                           "#B5413F")) +
  ## change the scale/labels of the steak-wellness variable (x-axis)
  function_name(limits = levels(fct_rev(pref$steak_pref)),
                labels = c("Well", 
                           "Medium Well" = "Medium-well",
                           "Medium",
                           "Medium rare"="Medium-rare",
                           "Rare")) +
  ## change the scale/lables of the percent axis (y-axis)
  function_name(labels = scales::percent, 
                expand = c(mult = c(0,0), 
                           add = c(0,0.035))) +
  ## change the title, subtitle, and caption
  function_name(title="'How Do You Like Your Steak Prepared?'", 
                subtitle="From a survey of 432 steak-eating Americans",
                caption="FiveThirtyEight: Surveymonkey") +
  ## change the theme (use ggthemes)
  function_name() +
  ## fine tune the theme
  function_name(axis.text = element_text(size = 14), 
                title = element_text(size = 16), 
                legend.position="none", 
                plot.caption=element_text(size = 12), 
                panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(),
                axis.text.x = element_blank() 
  )

p
```

## Save the Plot

```{r save-plot, warning=FALSE}
## save plot to figures/explanatory_figures directory
ggsave(plot = OBJECT_NAME, filename = FILENAME, width = 8, height = 4)
```

## Visualize the Data

```{r meat-plot, warning=FALSE} 
### Explore the data -- create your own plot!

```

## Save this plot 

```{r save-meat-plot, warning=FALSE}
## save plot to figures/explanatory_figures directory
ggsave(plot = OBJECT_NAME, filename = DIFFERENT_FILENAME)
```
