---
title: "Cleaning Data Project"
author: "DataTrail Team"
output: html_notebook
---

# Cleaning Data Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?> 

## Set up 

Let's load these packages for use. 

```{r}
## you can add more, or change...these are suggestions
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

## Set up directories

Here we are going to make a data directory if it doesn't already exist. 

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```


## Get the data 

We are going to use two different country datasets from Kaggle. 

This UN data-derived dataset: https://www.kaggle.com/datasets/sudalairajkumar/undata-country-profiles
The resulting CSV file is called `country_profile_variables.csv`.

This US government-derived dataset: 
https://www.kaggle.com/datasets/fernandol/countries-of-the-world
The resulting CSV file is called `countries of the world.csv`.

Both datasets have been downloaded and placed in the `data` and `raw` folder. Use readr::read_csv function to reach each dataset in. Call the first one `un_df` and the second `us_gov_df`. 

```{r}
# Read in the dataset for un_df
un_df <- read_csv(file.path("data", "raw", "country_profile_variables.csv"))
```

```{r}
# Read in the dataset for us_gov_df
us_gov_df <- read_csv(file.path("data", "raw", "countries of the world.csv"))
```

Use functions we have discussed previously to see what variables are in both `un_df` and `us_gov_df`. 

```{r}
colnames(un_df)
```
```{r}
colnames(us_gov_df)
```

### Cleaning the datasets 

You'll notice both datasets have pretty messy looking column names that are annoying to use. Use the `janitor::clean_names()` function to clean these up. 

```{r}
un_df <- janitor::clean_names(un_df)
us_gov_df <- janitor::clean_names(us_gov_df)
```

#### Clean up us_gov_df

You'll notice some of the variables in `us_gov_df` have commas `,` where really we would normally put decimals `.`. 

```{r}

```
