---
title: "Cleaning Data Project"
author: "DataTrail Team"
output: html_notebook
---

# Cleaning Data Project

## The goal of this analysis

<Write here what the goal of this analysis is. What question are we trying to answer?> 

## Set up 

Let's load these packages for use. 

```{r}
## you can add more, or change...these are suggestions
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

## Set up directories

Here we are going to make a data directory if it doesn't already exist. 

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```

## Getting the data 

Download this dataset and get it into R Studio: https://www.kaggle.com/datasets/fernandol/countries-of-the-world

You can use the link, download it, once you get the file, read the dataset in using `read_csv()` and assign it the name `countries`.

```{r}
countries_df <- read_csv(file.path("data", "countries_of_the_world.csv"))
```

Use `colnames()` function to see what column names we are dealing with in this dataset. 

```{r}
colnames(countries_df)
```
### Neaten column names 

To start, make it so all column names only have lower case letters. 

```{r}
countries_df <- countries_df %>% 
  rename_all(tolower) 
```

Now anywhere that says `%` replace with `perc`

```{r}
countries_df <- countries_df %>% 
  rename_all(~str_replace_all(., "%", "perc"))
```

### Treat numeric data as numeric data 

You'll notice a number of these variables are numeric, but because they use commas `,` where in the US we would use a decimal `.`, R thinks that they are characters. 

Use `mutate()` and `str_replace_all()` to replace `,` with `.` in these variables and then coerce them to be numeric. 

```{r}
mutate_at(vars(pop_density_per_sq_mi,
               countries_df$coastline_coast_to_area_ratio, 
```



